Determinants of Soccer Players' Market Values in Major European League(s)

### 2024-12-04 paper/paper.qmd
Final Update!

This section summarizes the key findings from the league-specific regression analyses, emphasizing only significant predictors of market value. Insignificant estimates, such as national team rankings and most position-specific coefficients, are excluded from this section but are included in the appendix.

@@

## Model Results

>>>>

This section summarizes the key findings from the league-specific regression analyses, emphasizing only significant predictors of market value. Insignificant estimates, such as national team rankings and most position-specific coefficients, are excluded from this section but are included in @sec-full.

@@

## Detailed Model Results{#sec-full}
